---
title: "backpack_predict_rmse driven"
author: "WangYong"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 119
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)

library(tidymodels)

library(bonsai)
library(lightgbm)
```

# 1. Define Problem

Welcome to the 2025 Kaggle Playground Series! We plan to continue in the spirit of previous playgrounds, providing
interesting and approachable datasets for our community to practice their machine learning skills, and anticipate a
competition each month.

## The Goal:

### original goal: Predict the price of backpacks given various attributes.

According the the dicusion forum, the data looks just noise. On,Feb 4th 2025, the lowest score on leaderboard is about
38.85851, the 50th score is 39.08183. I submitted the original sample submission.csv as baseline with 39.16456 rmse
score. The sample_submission.csv price column are are 81.411 which are same for all row.

### interim goal: improve score by EDA and linear model

note: long training time for the large data is complained in the dicussion forum as well. considering heavy noice and
limited rmse range(38.85\~39.16)

## the dataset files

The dataset for this competition (both train and test) was generated from a deep learning model trained on the Student
Bag Price Prediction Dataset dataset. Feature distributions are close to, but not exactly the same, as the original.
Feel free to use the original dataset as part of this competition, both to explore differences as well as to see
whether incorporating the original in training improves model performance.

Files train.csv - the training dataset; Price is the target train_extra.csv - a whole lot more training data! it should
be an interesting file. As it was added after complained by data noise and meaningless.

test.csv - the test dataset; your objective is to predict the Price for each row sample_submission.csv - a sample
submission file in the correct format.

# 2. Measure -RMSE

Root Mean Squared Error (RMSE) Submissions are scored on the root mean squared error. RMSE is defined as:
$\text{RMSE} = \sqrt{\frac{1}{n} \sum_{i=1}^{n} (y_i - \hat{y}_i)^2}$。

Submission File For each id in the test set, you must predict the Price of the backpack. The file should contain a
header and have the following format:

id,Price

300000,81.411

300001,81.411

300002,81.411

etc.

# 3. Analysis
## 3.1 load data and skim them
```{r}
get_raw_data <- function(file_name, col_types = cols()) {
  data_path <- '../input/playground-series-s5e2'
  full_name <- file.path(data_path, file_name)
  df <- 
    read_csv(full_name, col_types = col_types)|>
    mutate(across(where(is.character), as.factor))
  return(df)
}


raw_train <- get_raw_data('train.csv')
raw_train_ext <- get_raw_data('training_extra.csv')
raw_test <- get_raw_data('test.csv')
raw_submission <- get_raw_data('sample_submission.csv')
all_raw_dfs <- list( train=raw_train,
                    train_ext = raw_train_ext,
                    test = raw_test,
                    submission = raw_submission )
```

## 3.2 quick skim
```{r}
all_raw_df |>
  map(\(x) skim(x))


```

# Improve Rmse score(minimize)

# Control - Reproduciable
